\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-12-04 background.tex
updated some figs (pos)
Fixed some commenting issues in the figures

\begin{figure}[t!]
% \centering
\begin{SubFloat}{\label{fig:2a}Simple SystemJ program}%...verbatim subfigure
\begin{minipage}[b]{1\linewidth}% a minipage to control the width...
		\begin{lstlisting}[style=sysj,morekeywords={abort,await,emit,present,trap,pause,exit,delay,suspend}]
{
int counter = 0;
while(true){
 abort(immediate A){
  while(true) pause; 
 } // abort end
  emit O;
  if(counter != 0) { // java computation leading to WCRT}
  ++counter;
 } // loop end
} // SystemJ CD end
\end{lstlisting}%
\end{minipage}%
\end{SubFloat}
\hspace{1.5cm}%
% \begin{SubFloat}[Black box]{\label{fig:2b}Logical time in SystemJ}%
% \includegraphics[scale=0.4]{moc}
% \end{SubFloat}%
% \vspace{-10pt}

>>>>

\begin{figure}[t!]
\centering
\begin{SubFloat}{\label{fig:2a}Simple SystemJ program}%...verbatim subfigure
\begin{minipage}[b]{1\linewidth}% a minipage to control the width...
		\begin{lstlisting}[style=sysj,morekeywords={abort,await,emit,present,trap,pause,exit,delay,suspend}]
{
int counter = 0;
while(true){
 abort(immediate A){
  while(true) pause; 
 } // abort end
  emit O;
  if(counter != 0) {/* java computation leading to WCRT */}
  ++counter;
 } // loop end
} // SystemJ CD end
\end{lstlisting}%
\end{minipage}%
\end{SubFloat}
%\hspace{1.5cm}%
% \begin{SubFloat}[Black box]{\label{fig:2b}Logical time in SystemJ}%
% \includegraphics[scale=0.4]{moc}
% \end{SubFloat}%
% \vspace{-10pt}

### 2013-12-04 motivation.tex
Fixed some commenting issues in the figures

% system{
%  interface{
%   input signal TOUCH;
%   output signal GREEN_LIGHT;
%   output char channel S;
%   input char channel R;
%  }
\begin{figure}[t!]
% \begin{center}
	\vspace{-10pt}
		\begin{lstlisting}[style=sysj,morekeywords={sustain,send,receive,abort,await,emit,present,trap,pause,exit,delay,suspend}]
{ // Clock-domain 1
while(true) {
  trap(TRAP){
   // Abort if user touches the screen
   abort(TOUCH){
    {sustain GREEN_LIGHT;} //reaction R1
    || // synchronous parallel operator
    {
     //exit after any where from 50.3 to 200.3 ms.
     delay (50.3 .. 200.3 ms); 
     exit(TRAP); 
    } // reaction R2
   } do {send S(1);} // Send 1 if touched 
  } do {send S(0);} // Else Send 0
  pause; // only construct to consume logical time
 }
}
>< // asynchronous operator
{ // Clock-domain 2
  while(true){ receive S; // do something with S}
}
\end{lstlisting}
\caption{An example human responsiveness system (HRTCS)}
% }
% \end{center}
\label{fig:1}
\end{figure}

>>>>

% system{
%  interface{
%   input signal TOUCH;
%   output signal GREEN_LIGHT;
%   output char channel S;
%   input char channel R;
%  }
\begin{figure}[t!]
% \begin{center}
	\vspace{-10pt}
		\begin{lstlisting}[style=sysj,morekeywords={sustain,send,receive,abort,await,emit,present,trap,pause,exit,delay,suspend}]
{ // Clock-domain 1
while(true) {
  trap(TRAP){
   // Abort if user touches the screen
   abort(TOUCH){
    {sustain GREEN_LIGHT;} //reaction R1
    || // synchronous parallel operator
    {
     //exit after any where from 50.3 to 200.3 ms.
     delay (50.3 .. 200.3 ms); 
     exit(TRAP); 
    } // reaction R2
   } do {send S(1);} // Send 1 if touched 
  } do {send S(0);} // Else Send 0
  pause; // only construct to consume logical time
 }
}
>< // asynchronous operator
{ // Clock-domain 2
  while(true){ receive S; /* do something with S */}
}
\end{lstlisting}
\caption{An example human responsiveness system (HRTCS)}
% }
% \end{center}
\label{fig:1}
\end{figure}
